Method to infer relatedness using low coverage ancient DNA

### 2022-02-03 paper_overleaf/main.tex
Updates from Overleaf

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/ROHplot.png}
    \caption{Estimation of ROH probabilities along the genome. Top panel shows proportion of differences along the genome, and the bottom panel shows probability of seeing no ROH. (A) Simulation with no ascertainment, contamination, or ROH. (B) Simulation with ROH. (C) Simulation with ROH and ascertainment. (D) Simulation with ROH and contamination. Legend to be added with inkscape: blue:4x, green:0.5x, orange:0.2x}
    \label{fig:galaxy}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/fil0_relatable_plot.png}
    \caption{Application of KIn on Neandertal specimens from Chagyrskaya. Color of a square represents the relatedness, while the number denotes loglikelihood ratio.}
    \label{fig5}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{plots/inkscape_finalImg/ROHplot.png}
    \caption{Estimation of ROH probabilities along the genome in simulations with different cases of ROH, contamination, and ascertainment. Top panel shows proportion of differences in a simulated individual along the genome, and the bottom panel shows probability of seeing no ROH. (A) Simulation with no ascertainment, contamination, or ROH. (B) Simulation with ROH. (C) Simulation with ROH and ascertainment. (D) Simulation with ROH and contamination.}
    \label{fig:galaxy}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{plots/plotimg/fil0_relatable_plot.png}
    \caption{Application of KIn on Neandertal specimens from Chagyrskaya. Color of a square represents the relatedness, while the number denotes loglikelihood ratio between the two maximum likelihood models.}
    \label{fig5}
\end{figure}
